Verifying Demonstrations

### 2018-05-24 paper/analysis-security.tex
WIP on security analysis: temporal and spatial left

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\) and a signature
\begin{multline*}
\pi_{\pid'} = \SPK\mleft\{ (\sk') : \mright. \\
  \begin{aligned}
    \pid' &= \ACprf[_{\sk'}][\cid], \\
    \sigma &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk']] \mright\}
  \end{aligned} \\
    (\cid, \pid', \wid', t_s, t_s', l, \wsig').
\end{multline*}
\daniel{There are several approaches for Alice to do this, \eg attacking the 
  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
  I think we should describe them.}

@@

\subsection{Verifying the participation count}

\daniel{Rewrite!}
There are three parts to verifying the participation count.
First, we must verify the eligibility of each proof, \ie of all its shares.
Second, we must count these valid proofs.
Third, each protester must check that their proof is indeed registered so that 
it can be counted.

\subsubsection{Eligibility and universal verifiability}

\daniel{Do actual security analysis.}
Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
to count the valid proofs.
To do this we must be able to verify the eligibility of a proof (\ie of all 
its shares) and then count it if valid.
To verify the eligibility of a proof share, we must verify that \(\pid\), \(\wid\) 
and \(\wsig\) are not just randomly generated numbers but they actually depend on 
the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
We will do this with \ac{NIZK} proofs.

\subsubsection{Individual verifiability}

\daniel{Do actual security analysis.
  This is reduced to the security of the blockchain.}
The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
an adversary from dropping participation proofs.
Thus each protester must verify that their own proof is indeed included.
After Alice commited to her proof (share) in the blockchain, she stores the hash 
of the block.
At a later time, she can still verify that the block is indeed still there.
At this point, this hash value is the only thing she must store for individual 
verifiability.

>>>>

\subsection{Individual and universal verifiability}%
\label{analysis-individual}%
\label{analysis-universal}

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (proof shares) are indeed included.
As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \wsig, 
  \pi_\pid, \pi_{\wid, \wsig}\)) are committed to the blockchain and available 
from public storage (see \cref{fig:ProtocolOverview}).
Alice and Bob can simply check that all of their proof shares are indeed there 
and thus the security of individual verifiability depends on the properties of 
the blockchain and storage.

\Cref{UniversalVerif} requires that also anyone can verify the result and that 
all participation proofs counted indeed are eligible.
As the proof shares are committed and stored publicly, anyone can download them, 
verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid, \wsig}\)) the proofs and 
count them.
As for individual verifiability, the security of universal verifiability is 
reduced to the properties of the blockchain and storage but also the eligibility 
verification, which we will discuss next.

\subsection{Eligibility verifiability}%
\label{analysis-eligibility}

\Cref{EligibilityVerif} states that anyone must be able to determine the 
authenticity of the relevant attributes of the data.
We have several attributes that must be verifiable:
time of creation (temporal eligibility),
physical location of \(\sk_P\) at creation (spatial eligibility),
recognize two proofs from the same person (one-proof-per-person eligibility) and 
that the proof is indeed designated for the event (designated-event 
eligibility).
We will now analyse these.

@@

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\) and two signatures:
\begin{multline*}
\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
  \begin{aligned}
    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
  \end{aligned} \\
    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
\end{multline*}
and
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid'] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid', \wid', t_s, t_s', l, \wsig').
\end{multline*}

\daniel{There are several approaches for Alice to do this, \eg attacking the 
  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
  I think we should describe them.}
